Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
new version

---
title: One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies.]
date: 17 February 2023
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
fontsize: 12pt
mainfont: Times New Roman
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage[T1]{fontenc}
   - \usepackage[utf8]{inputenc}
   - |
    \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
    \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem. We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches. To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they speak and when. Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985. We find that presidents often construct the Amazon as an environmental problem when speaking far away from the Amazon, whereas they usually construct it as economic or social problems when in the Amazon. Furthermore, presidents increasingly construct the Amazon as multiple problems rather than only economic or environmental problems.
---

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 8190 (including abstract, text, references, and footnotes)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

The Brazilian Amazon, which covers around 60% of the whole biome, is home to over 28 million people. The Rainforest spans over seven international borders and contains enormous amounts of highly valued minerals such as iron ore and gold. Its most inhabited city, Manaus, enjoys a distinct fiscal regime designed to create jobs in the region and connect its economy to the rest of the country. At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas. The Brazilian Amazon is, thus, a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed in the literature about policies in the Amazon as having a single understanding of what the Amazon problem is and consequently, proposing coherent policies for the region. Although it is helpful to compare variation across different governments, this analysis oversimplifies policies and discourse within governments misrepresenting what, in reality, is more intricate and inconsistent. In this article, we ask how has the Amazon been constructed as a political problem since 1985?

We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as Presidents, construct objects of policies as particular problems depending on where and when they participate in politics. To examine this variation, we created a dataset containing 6240 official speeches by all Brazilian presidents since 1985. Drawing from the socio-cultural history of the Brazilian Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon. These problem-constructions relate to national sovereignty, economic integration, social development, or environmental conservation. We employ supervised machine learning to classify how the Amazon related statements construct it as a problem, and then conduct an inferential and descriptive analysis of the data. A systematic focus on presidential speeches is important because while many scholars recognize decisions to deforest on the ground are derived from what the government says and does [@capobianco2021; @campbell2015], we lack empirical accounts of the Amazon in presidential discourse.

We have four main findings. First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation. Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration. Second, presidents are more likely to construct the Amazon as an environmental conservation problem when environmental related issues are not urgent (e.g. lowering deforestation rates). When environmental related issues become more urgent (e.g. rising deforestation rates), presidents tend to side-step the issue and construct the Amazon as an issue of economic integration. Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses, but does not systematically change how the Amazon is constructed as a problem. Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.

Empirically, we contribute to the literature about the Amazon by providing the first overview of where, how, and when the Amazon has been constructed as a problem in presidential speeches. We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an aligned issue is. Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important actors behave differently inside and outside the country, by doing so we reveal how the Amazon as a problem varies in transnational politics. Conceptually, problem-constructions highlight the extent to which Amazonian problems are ignored or privileged in transnational politics, and avoids assumptions of the Amazon as a solely environmental problem.

This article is divided into 4 sections. First, we outline the connection between problem-constructions, transnationalism, and presidential speeches. Next, we present our research design including the description of our data and methodological approaches. In the third part, dedicated to the analysis, we display the results of our inferential models and move to explain developments in problem-constructions over time. We conclude by summarizing the empirical and conceptual contributions of the article.

# 2. Theory: problem-constructions, transnational settings, and problem urgency

@@

Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies and discourse [see @lopez2023; @fairfield2017; @poncedeleon2021] than suggested by the literature above. We argue that the reason behind monolithic representations of governments in literature about the Amazon is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is. Because of the Amazon Rainforest role in global climate-mitigation, , and consequently, as an environmental problem. If the Amazon is thought of as an environmental problem, then it demands an environmental solution. The Amazon region, its peoples, and forests, though, are a historically complex object of policies that comprise economic, social, and sovereignty concerns.

@@

Following Bacchi, we place discourse about policy objects at the center of our conceptual framework. We define policy objects as objects that demand dedicated political attention and argue that by deciding to speak about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem. The problem might be either explicitly stated, or implicitly hidden in the underlined solution. This is what we label as problem-constructions.

Presidential discourses are a good instance to identify problem-constructions over time. Presidential speeches and policy share a co-constitutive relationship as speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004]. This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution [@macaulay2017]. In Brazil's hybrid system, often referred to as a Coalitional Presidentialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies. This means that presidents often have enough power and support to implement the agenda they deem appropriate. We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.

## 2.2 Transnational settings, urgency, and variation in problem-constructions

The possibility of different problem-constructions for the same policy object in political discourse requires an explanation of why they vary. There are two potential theories for explaining variation in problem-construction in international/transnational politics: Putnam's two-level game and Keck and Sikkink's transnational networks.

@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests of domestic and international groups. At the national level, interest groups pressure the government to adopt favorable policies. Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988 p. 434]. The theory has been expanded to cover multi-levels games [@collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups. Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups. Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found supporting evidence that location does not change the content of the speech, but can lead presidents to side-step the issue.

The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups. This view seems incompatible with the possibility of contradictory policies and of varied problem-constructions. Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, from the local level to the international level [@nye1971; @keck1998]. In this context, international summits are considered a transnational setting because non-state actors participate in and shape them. We view, for instance, summits as the United Nations Framework Convention of Climate Change (UNFCCC) not only as a purely intergovernmental body, but as a transnational space composed of international media, corporations, non-governmental organizations, and social movements.

While @keck1998 theory is developed in the context of value-based advocacy groups, hence non-state actors, the overall view of international politics holds for state actors. Their theory rejects the dichotomy of international and domestic levels and argues that the identity and goals of transnational actors are not derived from their structural location vis-a-vis domestic and foreign interest groups. Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p. 4]: state and non-state actors participate in and shape international politics.

Important participants of transnational networks, as presidents, can use a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors. They can create politically meaningful information and/or move it where they believe it can have an impact [@keck1998, p. 24]. They can also leverage institutions to realize symbolic or material gains. In this sense, the positions of actors in transnational networks derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.

Problem-constructions are choices transnational actors have of how to represent objects of policies as problems. If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors', as presidents, choice of problem-constructions depend on their views of an audience at a certain period. Specifically, how urgent a problem is in a certain space and/or at a certain time.

@@

Transnational actors construct problems and attempt to inform and/or leverage audiences for symbolic or material gains according to their expectations of that audience. We conceptualize space in terms of settings. Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study. This indicates how transnational actors construct policy objects as problems can vary, for instance, within the country --- speaking inside the Amazon region versus outside --- because presidents identify these audiences as distinct. The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where presidents' expectations and identities of an audience could diverge completely from that of domestic actors. In each one of these settings different problems might be more urgent and the president's expectations about what can be leveraged for material and symbolic gains might influence how a problem is implicitly or explicitly constructed.

@@

How presidents construct policy objects varies over time as the urgency of certain problems changes not only across settings but in time as new information arises. We conceptualize time as the urgency of a broad and related issues to those surrounding a policy object. This is largely defined by factors exogenous to the speaker. This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider mentioning climate change when discussing various forms of public policy. For instance, when speaking about subsidies for fossil fuel companies in the 1980s, presidents would likely not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased relevance of the topic.

While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, certain transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time. Accordingly, certain transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.

Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions. We help to advance the literature about the Amazon in three main ways. First, we provide an outlook of the region, its people, and forest beyond its environmental nature by focusing on different problem-constructions. In doing so, we take a step back and avoid assuming what type of problem the Amazon is. Instead, we focus on how the Amazon has been represented as a problem. Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both scenarios [@hochstetler2007]. Our focus on presidential speeches afford us the analytical leverage to identify transnational variation, as speeches take place in multiple settings over time. Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017]. When it comes to the environment, studies tend to focus primarily on Bolsonaro's discourse [@marquardt2022; @mendes2022]. We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there is.

If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances. While there might exist convergences of priorities over time, as problems become more urgent, contradictions become possible. This does not mean that policies and priorities change instantaneously and consequently do not matter. Rather, presidents will focus on representing issues in forms aligned with what their perception of an audience are.

@@

To create a dataset containing all Brazilian presidential speeches, we update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022. The final dataset contains 6240 speeches with their date and state or country location. We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem "amazon". In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others. We find that 968 speeches are, at least partially, about the Amazon.

@@

## 3.1 Operationalizing Amazonian problem-constructions

We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development. While the three formers are present in the literature, we argue a fourth one exists in speeches: social development.

*National Sovereignty* In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p. 8], and secured the Amazon as Brazilian. While military diplomacy was very successful, the process did not come without its issues and sovereignty in the Amazon became one of the main military concerns[@rajao2020]. More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become more varied. Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors. The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and any foreign or non-state presence in the region can be part of a broad strategy to take the region. The policy solutions to the issue of sovereignty included the monitoring of the borders and strict regimes related to entry into the region.

*Economic Integration* The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005]. In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021]. First, it assumed that nature should be conquered by mankind. Second, it assumed that exploiting natural resources would render the Amazon region economically profitable. Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory. Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry. The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized. These policy solutions have at their core the development of the necessary infrastructure to integrate the region into the national and international economy.

*Environmental Conservation* The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006]. The creation of these institutions stemmed from the impression of the lack of control over the environment, following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990]. This process accelerated in the late 1980s with the birth of modern environmentalism [@viola1987]. The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted. The policy solutions imply, for example, further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.

*Social Development* As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights. Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights. However, such emphasis can be masked within both the economic integration and environmental conservation accounts. While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected. Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity. The policy solutions imply enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.

An Amazonian statement can be coded as referring to multiple problem-constructions (see Figure 1 below). Amazonian statements, thus, can be pure-type statements (i.e. they construct the Amazon as a single problem) or mixed-types (i.e. they construct the Amazon as multiple issues).

@@

We randomly select a sample of 1024 Amazonian statements (50% of our data) and each author hand-codes it separately. Once manual coding was finished, the average intercoder agreement was 86%, the authors resolved disagreements through discussion and refined the codebook (see appendix). We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations) to train a machine learning algorithm. We chose to hand code half of the observations because there are several nuances in how presidents talk about the Amazon over time, and thus the training set size should be increased [see @grimmer2022].

We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text. The model was validated by testing it on the validation set. As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would. The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1]. Automating the code saved the authors about two months.

@@

## 3.2 Operationalizing settings and urgency

Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of an aligned issue. This comprises our independent variables.

>>>>

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  word_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  pdf_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem. We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches. To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985. We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
---

```{=latex}
\keywords{ discourse analysis, presidential speeches, transnational governance, environmental policy, Brazilian Amazon, supervised learning}
```
```{=latex}
\wordcount{ 7900 (including text, endnotes, footnotes and references)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

The Brazilian Amazon, which covers around 60% of the whole biome, is home to over 28 million people. The Rainforest spans over seven international borders. Its most inhabited city, Manaus, enjoys a distinct fiscal regime designed to create jobs in the region and connect its economy to the rest of the country. At the same time, an extensive portion of the Brazilian Amazon is protected by a combination of indigenous territories and protected areas, rendering it an important component of global climate mitigation. The Brazilian Amazon is, thus, a complex object of policy as it comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, the literature about policies in the Amazon often portray governments as having a single understanding of what the Amazon problem is and, consequently, proposing coherent policies for the region. Although this literature is helpful to compare variation across different governments, such analyses oversimplifies policies within governments misrepresenting what, in reality, is more intricate and inconsistent. In this article, we ask how has the Amazon been constructed as a political problem since 1985?

We combine @bacchi1999's theory of problem representation and @keck1998's theory of transnationalism to develop a framework outlining how transnational actors, as presidents, construct objects of policies as particular problems depending on where and when they participate in politics. To examine this variation, we created a dataset containing 6240 official speeches by all Brazilian presidents since 1985. Drawing from the socio-cultural history of the Amazon, we inductively developed a codebook to categorize problems related to political concerns over the Amazon. These problem-constructions touch upon national sovereignty, economic integration, social development, or environmental conservation. We employ supervised machine learning to classify how Amazon related statements construct the Amazon as a problem. We then conduct an inferential and descriptive analysis of the data. A systematic focus on presidential speeches is important because many scholars recognize decisions to deforest on the ground are derived from government's policies and discourse [@capobianco2021; @campbell2015]. Still, we lack empirical accounts of the Amazon in presidential discourse.

We have four main findings. First, when presidents are far away from the Amazon region, they are more likely to construct the Amazon as an issue of environmental conservation. Within the Amazonian region, presidents usually construct the Amazon as an issue of social development and economic integration. Second, presidents are more likely to construct the Amazon as an environmental conservation problem when deforestation rates decrease. When deforestation rates increase, presidents tend to side-step the issue and construct the Amazon as an issue of economic integration. Third, we find that high-profile environmental events, which receive strong international media attention, drive up the frequency at which the Amazon appears in discourses. However, these events does not systematically change how the Amazon is constructed as a problem. Finally, we find that presidents are increasingly more likely to mix problem-constructions and construct the Amazon as a complex and multifaceted object of policy.

Empirically, we contribute to the literature about the Amazon by providing the first overview of where, how, and when the Amazon has been constructed as a problem in presidential speeches. Analyses of Brazilian environmental discourse and policies do not adopt methodological strategies that distinguish how important transnational actors behave differently inside and outside the country. We show how the same government constructs the Amazon as a different problem depending on where they speak and how urgent an issue is. Conceptually, problem-constructions highlight the extent to which Amazonian problems are ignored or privileged in transnational politics, and avoids assumptions of the Amazon as a solely environmental problem.

We divide this article into four sections. First, we outline the connection between problem-constructions, transnationalism, and presidential speeches. Next, we present our research design including the description of our data and methodological approaches. In the third part, dedicated to the analysis, we display the results of our inferential models and move to explain developments in problem-constructions over time. We conclude by summarizing the empirical and conceptual contributions of the article.

# 2. Theory: problem-construction and transnationalism

@@

Elsewhere, social scientists have shown that there is more variation and contradiction within a specific government's policies than suggested by the literature above [see @lopez2023; @fairfield2017; @poncedeleon2021]. We argue that the reason behind these monolithic representations of governments is conceptual: many studies of the region contain an explicit or implicit assumption of what the "Amazon problem" is. Because of the Amazon Rainforest role in global climate-mitigation, the Amazon is often assumed to be an environmental problem that demands environmental solutions. The Amazon region, its peoples, and forests, though, are a historically complex object of policies that also comprise economic, social, and sovereignty concerns.

@@

Following Bacchi, we place discourse about policy objects at the center of our conceptual framework. We define policy objects as objects that demand dedicated political attention and argue that by speaking about a policy object, governments are making a deliberate choice to represent, or construct it, as a specific problem. The problem might be either explicitly stated, or implicitly hidden in the underlined solution. This is what we label as problem-constructions.

Presidential discourses are a good instance to identify problem-constructions over time and across spaces. Presidential speeches and policy share a co-constitutive relationship as speeches have the power to introduce, define, and justify public policy, as well as shape issue perception to broad audiences [@zarefsky2004]. This is particularly true in the Brazilian context where the executive branch of government, led by the president, has historically been the primary player in shaping public policy, especially after the 1988 constitution [@macaulay2017]. In Brazil's hybrid system, often referred to as a Coalitional Presidentialism [@couto2021], presidents build legislative support for a broad agenda through the distribution of positions in the state bureaucracies. They also have vast decree powers to adopt policy unilaterally[@pereira2008]. This means that presidents often have enough power and support to implement the agenda they deem appropriate, especially in the case of climate change[@hochstetler2021]. We thus consider presidential speeches an adequate instance to identify various problem-constructions for the same policy object.

## 2.2 Settings, urgency and variation in problem-constructions

The possibility of different problem-constructions for the same policy object requires an explanation of why they vary. There are two potential theories for explaining variation in problem-construction in international/transnational politics: Putnam's two-level game and Keck and Sikkink's transnational networks.

@putnam1988 argues that the outcomes of international negotiations lie within the overlap between the interests of domestic and international groups. At the national level, interest groups pressure the government to adopt favorable policies. Internationally, the government seeks to fulfill domestic preferences "while minimizing the adverse consequences of foreign developments" [@putnam1988 p. 434]. The theory has been expanded to cover multi-levels games [see @collinson1999], but its core remains the same: the outcome of negotiations should lie within the overlap of distinct interest groups. Consequently, presidential speeches are not necessarily contradictory across venues but a common denominator of the interests of different groups. Adopting two-level games to explain American presidential speeches about climate change, @calderwood2020 found little support that location changes the content of presidential speeches.

The two-level game theory implies that actors respond rationally to systemic pressures imposed by their position in relation to interest groups. This view seems incompatible with the possibility of varied problem-constructions for the same policy object. Rather, we start from the idea of transnationalism as relationships that transcends nation-states and incorporates non-state actors, from the local level to the international level [@nye1971; @keck1998]. In this context, international summits, for example, are considered a transnational space because they are composed of international media, corporations, non-governmental organizations, social movements, and various state actors.

Although @keck1998's theory is developed in the context of value-based advocacy groups( i.e. non-state actors), the overall view of international politics holds for state and other non-state actors. Their theory rejects the dichotomy of international and domestic levels and argues that the identity and goals of transnational actors are not derived from their structural location vis-a-vis domestic and foreign interest groups. Rather, international politics as transnational networks have "a structured and structuring dimension" [@keck1998, p. 4]: state and non-state actors participate in and shape international politics.

Important participants of transnational networks, as presidents, can use a myriad of tactics to introduce, define, persuade, socialize, and pressure when interacting with other actors. They can create politically meaningful information and move it where they believe it can have an impact or leverage institutions to realize symbolic or material gains[@keck1998]. In this sense, the positions of actors in transnational networks derive from complex interactions in which their identities and goals are malleable and can vary depending on the space and time of the interaction.

Problem-constructions are choices transnational actors have of how to represent objects of policies as problems. If malleable identities across space and time are a defining feature of transnational politics, it follows that transnational actors' choice of problem-constructions depend on their views of an audience at a certain period. Specifically, how urgent a problem is in a certain space or at a certain time.

@@

Transnational actors construct problems and attempt to inform or leverage audiences for symbolic and material gains according to their expectations of that audience. We conceptualize space in terms of settings. Settings are levels of aggregation for transnational audiences that make sense in light of the object of policy under study. This indicates how transnational actors construct policy objects as problems can vary for instance, within the country --- speaking inside the Amazon region versus outside --- because transnational actors identify these audiences as distinct. The same holds true when speaking abroad --- in Amazonian countries, non-Amazonian countries, and at international summits --- where transnational actors' expectations and identities of an audience could diverge completely from that of domestic actors. In each one of these settings transnational actors' expectations might influence how a problem is implicitly or explicitly constructed.

@@

How transnational actors construct policy objects varies as the urgency of certain problems changes as new information arises over time. We conceptualize time as the urgency of broad and related issues to those surrounding a policy object. This is largely defined by factors exogenous to the speaker. This indicates, for instance, that as climate change becomes more urgent and mainstreamed as a broad issue, it is more likely that actors will consider mentioning climate change when discussing various forms of public policy. For instance, when speaking about subsidies for fossil fuel companies in the 1980s, presidents would likely not mention the dangers of climate change, whilst today, climate change would likely be mentioned given the increased relevance of the topic.

While time and space interact, here we are interested in their cumulative effects: when speaking in the 1990s to an audience that finds climate change urgent, transnational actors would likely mention it as a problem independently of the perceived urgency of a climate breakdown at the time. Accordingly, transnational actors might even consider touching upon the issue while speaking at a business association today, because of its urgency.

If our conceptual framework holds, it entails that transnational actors view different settings as distinct policymaking instances. While there might exist convergences of priorities over time, as problems become more urgent, contradictions are possible. This does not mean that policies and priorities change instantaneously and consequently do not matter. Rather, transnational actors will focus on representing issues based on their perception of an audience.

Our conceptual framework, thus, combines Bacchi's theory of problem-representation and Keck and Sikkink's theory of transnationalism to account for diverse problem-constructions in Brazilian presidential speeches. We help to advance the literature about the Amazon in three ways. First, we provide an outlook of the region, its people, and forest beyond its environmental nature. In doing so, we take a step back and avoid assuming what type of problem the Amazon is. Instead, we focus on how the Amazon has been represented as a problem. Second, many analyses of Brazilian environmental policies center on its national and international nature without adopting methodological strategies that distinguish how important actors behave differently in both policymaking instances. Our focus on presidential speeches afford us the analytical leverage to identify transnational variation, as speeches take place in multiple settings over time. Finally, presidential speeches in Brazil have been studied for topics such as race relations [@silva2019] and inequality [@grangeia2017]. When it comes to the environment, studies tend to focus primarily on Bolsonaro's discourse [@marquardt2022; @mendes2022]. We argue, however, that a longitudinal view across Brazilian presidents is important to understand how much continuity and change there is.

@@

## 3.1 Data

We update a dataset of all Brazilian presidential speeches from 1985 to 2019 [@cezar2020] to include speeches from 2020 to 2022. The final dataset contains 6240 speeches with their date and state or country location. We proceed to identify speeches that refer to the Amazon as a region, people, or forest, by detecting the stem "amazon". In Portuguese, the stem captures terms such as "Amazonia", "Amazonica", "Amazonidas", "Amazonense(s)", "Amazonas", among others. We find that 968 speeches are, at least partially, about the Amazon.

@@

## 3.2 Operationalizing Amazonian problem-constructions

We use a codebook developed through an inductive process and informed by the literature to categorize Amazonian statements into four problem-constructions: national sovereignty, economic integration, environmental conservation, and social development. While the three formers are present in the literature, we argue a fourth one exists: social development. Amazonian statements can construct the Amazon as a single problem ( i.e. pure-type statements), or can construct the amazon as referring to multiple problem-constructions (i.e. mixed-types), as Figure 1 (below) details.

*National Sovereignty*

In the process of securing Amazonian borders since the 18th century, Brazil thwarted "the imperial ambitions of France, Britain, the United States, Belgium, Bolivia, and Peru" [@hecht1990, p. 8], and secured most of the Amazon as Brazilian. While military diplomacy was very successful, the process did not come without its issues and sovereignty in the Amazon became one of the main military concerns[@rajao2020]. More recently, as we move to a world where non-state actors gain importance in international politics [@andonova2014; @keck1998], sovereignty-related problems become varied. Threats to national sovereignty, consequently, broaden from nation-states to a wide set of actors. The sovereignty problem-construction advances the view that the Brazilian Amazon belongs to Brazil and foreign or non-state presence in the region are concerning. The policy solutions that implicitly represent this problem include the monitoring of the borders and strict regimes related to entry into the region.

*Economic Integration*

The Vargas dictatorship (1937-46) and the military dictatorship (1964-89) took over the task of modernizing the Amazon [@becker2005]. In 1966, the Brazilian Military launched 'Operation Amazon', a policy to modernize the region based on three assumptions [@acker2021]. First, it assumed that nature should be conquered by mankind. Second, it assumed that exploiting natural resources would render the Amazon region economically profitable. Third, it assumed that populating the region was necessary to integrate it into the country and exert control over the territory. Concretely, this meant a series of major infrastructure projects, incentives for settlers to expand the agricultural frontier, and the establishment of a tax-free zone in Manaus to attract industry. The economic integration problem-construction advances the view that the Brazilian Amazon needs to be developed and modernized. These policy solutions have at their core the development of the necessary infrastructure (physical and fiscal) to integrate the region into the economy.

*Environmental Conservation*

The rapid economic changes in the region from the 1960s to the 1980s were matched with the birth of domestic environmental institutions [@drummond2006]. The creation of these institutions stemmed from the impression of the lack of control over the environment, following the efforts to economically integrate in the region [@acker2021; @capobianco2021; @hecht1990]. This process accelerated in the late 1980s with the new forms of environmentalism [@viola1987]. The environmental conservation problem-construction emphasizes that the Amazon should be preserved by the creation of protected areas and deforestation should be halted. The policy solutions imply further investments in command-and-control institutions, the valuation of standing ecosystems through incentive schemes, and the creation of protected areas.

*Social Development*

As democracy established itself in Brazil, especially with the 1988 constitution, settlers in the Amazon became electorates with constitutional rights. Governments can emphasize the lack of hospitals, sanitation, and schools concerning peoples' dignity, standards of living, and other constitutional rights. However, such emphasis can be masked within both the economic integration and environmental conservation accounts. While for some groups, such as indigenous peoples, constitutional rights and preservation of the forest go hand in hand, providing better standards of living to large portions of populations of the Amazonian states and conservation are not necessarily connected. Social development is a problem-construction that focuses on constitutional rights, citizenship, and dignity. The policy solutions imply enabling access to water, sanitation, electricity, internet, and radio, as well as the construction of schools and hospitals.

@@

We randomly selected a sample of 1024 Amazonian statements (50% of our data) and each author hand-coded these separately. Once manual coding was finished, the authors resolved disagreements through discussion and refined the codebook (in appendix). We then randomly divided the hand-coded data into a training set (80% of observations) and validation set (20% of observations) to train a machine learning algorithm. We chose to hand code half of the observations because there are multiple categories of how presidents talk about the Amazon, and the training set size should be increased [see @grimmer2022].

We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text. The model was validated by testing it on the validation set. As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would. The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1]. Automating the code saved the authors over one month of work.

@@

## 3.3 Operationalizing settings and urgency

Our explanation for variation in problem-constructions is based on the setting of a speech and the urgency of issues. This comprises our independent variables.
